Optimization Methods for Parameter Identifications \\ in Settings with Only Partial Knowledge

### 2023-06-06 presentation/phd_defense_pres.tex
PhD defense version 1

\usepackage{xspace}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{lmodern}
\newcommand{\themename}{\textbf{\textsc{metropolis}}\xspace}
\newcommand{\ouralgo}{\ensuremath{\mathcal{MSR}3}}
%\title{PhD Defense}
%\date{\today}
%\author{Aleksei Sholokhov}
%\titlegraphic{\includegraphics[width=0.5\textwidth]{Figures/UW_amath.pdf}\hspace{3em}\includegraphics[height=1cm]{Figures/IHME_Logo.jpg}}
\title{$\mathcal{MSR}3$ -- Sparse Relaxed Regularized Regression for Linear Mixed-Effect Models}
\date{\today}
\author{Aleksei Sholokhov \\ \vspace{1em}  Together with James V. Burke, Peng Zheng, Damian Santomauro, \\ and Aleksandr Aravkin}
\titlegraphic{\includegraphics[width=0.5\textwidth]{Figures/UW_amath.pdf}\hspace{3em}\includegraphics[height=1cm]{Figures/IHME_Logo.jpg}}

%\AtBeginSection[]{
%  \begin{frame}
%  \vfill
%  \centering
%  \begin{beamercolorbox}[sep=8pt,center,shadow=true,rounded=true]{title}
%    \usebeamerfont{title}\insertsectionhead\par%
%  \end{beamercolorbox}
%  \vfill
%  \end{frame}
%}

@@

%\section{Introduction}
%\begin{frame}{Plan of the Defense}
%Show topics and published papers. Mention covid
%\end{frame}

@@

@@

\begin{frame}{Thank you!}
	\includegraphics[width=\textwidth]{Figures/pysr3_screenshot.png}
	The code is available on GitHub: \href{github.com/aksholokhov/pysr3}{https://github.com/aksholokhov/pysr3}\footfullcite{sholokhov2023pysr3}
	\begin{itemize}
		\item All estimators are fully compatible to \texttt{scikit-learn} library.
		\item Implements SR3 for linear, generalized-linear, and linear mixed-effect models.
		\item Has tutorials, tests, and documentation.
	\end{itemize}
\end{frame}

@@

\begin{frame}{Data-Driven Modeling of Physical Systems}

@@

\uncover<2->{
\begin{columns}[T,onlytextwidth]
\column{0.6\textwidth}
\textcolor{orange}{First-Principle Models}
\begin{itemize}
	\item Require extensive knowledge of the phenomenon
	\item Require a lot of compute for simulating large-scale phenomena
\end{itemize}
\column{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{Figures/NN.jpg}
\end{columns}
}
\vspace{2em}
\uncover<3->{
\begin{columns}[T,onlytextwidth]
\column{0.6\textwidth}
\textcolor{green}{Data-Driven Models}
\begin{itemize}
	\item Require a lot of data
	\item Often struggle to extrapolate
\end{itemize}
\column{0.4\textwidth}
\centering
\includegraphics[width=0.8\textwidth]{Figures/nn_schematics.pdf}
\end{columns}
}
\vspace{2em}
\uncover<4->{
\begin{columns}[T,onlytextwidth]
\column{0.6\textwidth}
\textcolor{blue}{Hybrid Models}
\begin{itemize}
	\item Incorporate elements of both approaches
	\item Supplement data with knowledge or priors
\end{itemize}
\column{0.4\textwidth}
\centering
\includegraphics[width=0.5\textwidth]{Figures/NS_pic.png}
\end{columns}

@@

\begin{frame}{Incorporating Knowledge of Physics into Neural Networks}
\begin{enumerate}
	\item<2-> \textbf{Symmetry Based:} incorporate symmetries and conservation laws as hard constraints into a network: E3NNs\footcite{geiger2022e3nn}, LieConv\footcite{Finzi2020}, RiCNN \footcite{chidester2018rotation}
	\item<3-> \textbf{Model Discovery Based:} use a library of terms to discover simple equations: SINDy\footcite{champion2019data}, Genetic Programming\footcite{schmidt2009distilling}
	\item<4-> \textbf{Equations Based:} incorporate first-principle models to aid training of networks: PINNs\footcite{raissi2017physics}, UDEs\footcite{rackauckas2020udes}
\end{enumerate}

@@

\begin{frame}{Physics-Informed Loss}
%1) We introduce physics to this system by adding a term which regularizes latent gradient field. 
%2) In particular, it forces it to be equal to what a true physics should be under such projection.
%3) We can not evaluate physics everywhere but we can at particular carefully-selected points. We call these points collocation points.
%4) We feed a lot of collocation points and ask a network to do interpolation 
Using chain rule:
\only<1>{\includegraphics[width=\textwidth]{Figures/collocations_1.png}}
\only<2>{\includegraphics[width=\textwidth]{Figures/collocations_2.png}}
\only<3>{\includegraphics[width=\textwidth]{Figures/collocations_3.png}}
\only<4>{\includegraphics[width=\textwidth]{Figures/collocations_4.png}}
\only<5>{\includegraphics[width=\textwidth]{Figures/collocations_5.png}}
\end{frame}

\begin{frame}{Physics-Informed, Data-Driven, and Hybrid Models}

@@

@@

\begin{frame}{Results: Burgers' Equation}
Burgers' Equation:
\begin{equation}
	\begin{split}
		& u_t  + uu_x = \nu u_{xx} \\
	    & u(-\pi, t) = u(\pi, t),\quad \forall t \in [0, T]
	\end{split}
\end{equation}
\uncover<2->{
\includegraphics[width=\textwidth]{Figures/burgers_examples_of_ics.pdf}
}
\uncover<3->{
\includegraphics[width=\textwidth]{Figures/example_burgers.pdf}
}

@@

\begin{frame}{Single-Pixel Imaging}
	% This is how SPI setup translates into Math
	\includegraphics[width=\textwidth]{Figures/spi_math.png}
\end{frame}

@@

\begin{frame}{Results: Burger's Equation}
	\uncover<1->{
	When we capture 32 samples per frame:
	\includegraphics[width=\textwidth]{Figures/cs_burgers_comparison_32.pdf}
	}
	\uncover<2->{
	When we capture 2 samples per frame:
	\includegraphics[width=\textwidth]{Figures/cs_burgers_comparison_2.pdf}
	}

@@

\begin{frame}{Results: Burger's Equation}
	\includegraphics[width=\textwidth]{Figures/cs_burgers_psnr.png}
\end{frame}

\begin{frame}[label=again]{Results: Kolmogorov Flow}
	\animategraphics[loop,width=\textwidth]{5}{Figures/kolm_example_anim_}{0}{19}
\end{frame}

@@

\begin{frame}{Results: Gas Monitoring}

\begin{frame}{Conclusion and Acknowledgments}

\appendix
\section{Appendix: $\mathcal{MSR}3$}
\begin{frame}{Designing an Algorithm}
	$G_{\nu,\eta}$ encodes both gradient of a Lagrangian (lines 1-2) and the complementarity condition (line 3):
	\eq{
		G_{\nu,\eta}((\beta,\gamma,v),(\tbeta,\tgamma)) := \begin{bmatrix}
			\nabla_\beta \LL(\beta, \gamma) + \eta(\beta-\tbeta) \\
			\nabla_\gamma \LL(\beta, \gamma) + \eta(\gamma-\tgamma) - v\\
			v \bigodot \gamma - \mu\textbf{1}
		\end{bmatrix}
	}
	We apply Newton method to $G$ while geometrically decreasing $\mu$. \\
\textbf{Lemma:} For every $(\mu,\eta) \in \R_+\times\R_{++}$,
\eq{
	&(\hat\beta,\hat\gamma) = \argmin_{(\beta,\gamma)}\LL_{\eta,\mu}((\beta, \gamma),(\tbeta, \tgamma)) \\
	& \iff \\
	& \exists \hat{v} \in \R_{+}^q \text{ s.t. } G_{\nu,\eta}((\beta,\gamma,\hat{v}),(\tbeta,\tgamma)) = 0
}
If $\mu > 0$, then $\hat{v} = -\nabla\phi_\mu(\hat{\gamma})$, and if $\mu = 0$, then $\hat{v}$ is the unique KKT multiplier associated with the constraint $0 \leq \gamma$.
\end{frame}

@@

>>>>

\usepackage{xspace}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{lmodern}
\newcommand{\themename}{\textbf{\textsc{metropolis}}\xspace}
\newcommand{\ouralgo}{\ensuremath{\mathcal{MSR}3}}
%\title{PhD Defense}
%\date{\today}
%\author{Aleksei Sholokhov}
%\titlegraphic{\includegraphics[width=0.5\textwidth]{Figures/UW_amath.pdf}\hspace{3em}\includegraphics[height=1cm]{Figures/IHME_Logo.jpg}}
\title{Optimization Methods for Parameter Identifications \\ in Settings with Only Partial Knowledge}
\subtitle{Ph.D. Defense}
\date{\today}
\author{Aleksei Sholokhov}
\titlegraphic{\vspace{3em}\includegraphics[width=0.5\textwidth]{Figures/UW_amath.pdf}}

\AtBeginSection[]{
  \begin{frame}
  \vfill
  \centering
  \begin{beamercolorbox}[sep=8pt,center,shadow=true,rounded=true]{title}
    \usebeamerfont{title}\insertsectionhead\par%
  \end{beamercolorbox}
  \vfill
  \end{frame}
}

@@

\begin{frame}{Plan of the Defense}
\uncover<2->{
\includegraphics[height=35pt]{figures/sasha.png}
\includegraphics[height=35pt]{figures/jim.jpg}
\includegraphics[height=35pt]{figures/peng.jpg}
}
\uncover<3->{
\includegraphics[height=35pt]{figures/hassan.jpg}
\includegraphics[height=35pt]{figures/saleh.jpeg}
\includegraphics[height=35pt]{figures/yuying.jpeg}
}
\uncover<4->{
\includegraphics[height=35pt]{figures/nathan.jpg}
\includegraphics[height=35pt]{figures/steve.jpeg}
\includegraphics[height=35pt]{figures/josh.jpg}
}

\vspace{1em}
\uncover<2->{
\textbf{Sparse Relaxed Regularized Regression for Linear Mixed-Effect Models}\\
{\small
Together with Aleksandr Aravkin, James Burke, Damian Santomauro, and Peng Zheng
\begin{itemize}
	\item \only<1-4>{``A Relaxation Approach to Feature Selection for Linear Mixed Effects Models''}\only<5->{\underline{\textcolor{teal}{``A Relaxation Approach to Feature Selection for Linear Mixed Effects Models''}}} \\ \textit{submitted to Journal of Computational and Graphical Statistics (JCGS)}
	\item ``Analysis of Relaxation Methods for Feature Selection in Mixed Effects Models'' \\ \textit{submitted to Journal of Computational Optimization and Applications (COAP)}
	\item ``\texttt{pysr3}: A Python Package for Spare Relaxed Regularized Regression'' \\ \textit{Journal of Open-Source Software (JOSS), 2023, ICCOPT 2022, SIAM OPT 2023}
\end{itemize}
}
}

\vspace{1em}
\uncover<3->{
\textbf{PINODE: Physics-Informed Neural ODEs}\\
{\small
Together with Hassan Mansour, Saleh Nabi, and Yuying Liu
\begin{itemize}
	\item ``Physics-Informed Koopman Network'' \\
	\textit{SIAM ADS 2023, arXiv:2211.09419}
	\item \only<1-4>{``Physics-Informed Neural ODE: Embedding Physics into Models using Collocation Points''}\only<5->{\underline{\textcolor{teal}{``Physics-Informed Neural ODE: Embedding Physics into Models using Collocation Points''}}} \\
	\textit{Submitted to Nature Special Issue on Physics-Informed Machine Learning}
\end{itemize}
}
}
\uncover<4->{
\vspace{1em}
\textbf{Single-Pixel Imaging with Reduced-Order Models}\\
{\small
Together with J. Nathan Kutz, Steven Brunton, Joshua Rapp, Hassan Mansour, and Saleh Nabi
\begin{itemize}
	\item \only<1-4>{``Single pixel imaging of spatio-temporal flows using differentiable latent dynamics''}\only<5->{\underline{\textcolor{teal}{``Single pixel imaging of spatio-temporal flows using differentiable latent dynamics''}}} \textit{in preparation}
\end{itemize}
}
}

@@

\begin{frame}{Designing an Algorithm}
	$G_{\nu,\eta}$ encodes both gradient of a Lagrangian (lines 1-2) and the complementarity condition (line 3):
	\eq{
		G_{\nu,\eta}((\beta,\gamma,v),(\tbeta,\tgamma)) := \begin{bmatrix}
			\nabla_\beta \LL(\beta, \gamma) + \eta(\beta-\tbeta) \\
			\nabla_\gamma \LL(\beta, \gamma) + \eta(\gamma-\tgamma) - v\\
			v \bigodot \gamma - \mu\textbf{1}
		\end{bmatrix}
	}
	We apply Newton method to $G$ while geometrically decreasing $\mu$. \\
\textbf{Lemma:} For every $(\mu,\eta) \in \R_+\times\R_{++}$,
\eq{
	&(\hat\beta,\hat\gamma) = \argmin_{(\beta,\gamma)}\LL_{\eta,\mu}((\beta, \gamma),(\tbeta, \tgamma)) \\
	& \iff \\
	& \exists \hat{v} \in \R_{+}^q \text{ s.t. } G_{\nu,\eta}((\beta,\gamma,\hat{v}),(\tbeta,\tgamma)) = 0
}
If $\mu > 0$, then $\hat{v} = -\nabla\phi_\mu(\hat{\gamma})$, and if $\mu = 0$, then $\hat{v}$ is the unique KKT multiplier associated with the constraint $0 \leq \gamma$.
\end{frame}

@@

\begin{frame}{Software}
	\includegraphics[width=\textwidth]{Figures/pysr3_screenshot.png}
	The code is available on GitHub: \href{github.com/aksholokhov/pysr3}{https://github.com/aksholokhov/pysr3}\footfullcite{sholokhov2023pysr3}
	\begin{itemize}
		\item All estimators are fully compatible to \texttt{scikit-learn} library.
		\item Implements SR3 for linear, generalized-linear, and linear mixed-effect models.
		\item Has tutorials, tests, and documentation.
	\end{itemize}
\end{frame}

@@

\begin{frame}{Modeling of Physical Systems}

@@

\uncover<2->{
\begin{columns}[T,onlytextwidth]
\column{0.6\textwidth}
\textcolor{orange}{First-Principle Models}
\begin{itemize}
	\item Require extensive knowledge of the phenomenon
	\item Require a lot of compute for simulating large-scale phenomena
\end{itemize}
\column{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{Figures/NN.jpg}
\end{columns}
}
\vspace{2em}
\uncover<3->{
\begin{columns}[T,onlytextwidth]
\column{0.6\textwidth}
\textcolor{teal}{Data-Driven Models}
\begin{itemize}
	\item Require a lot of data
	\item Often struggle to extrapolate
\end{itemize}
\column{0.4\textwidth}
\centering
\includegraphics[width=0.8\textwidth]{Figures/nn_schematics.pdf}
\end{columns}
}
\vspace{2em}
\uncover<4->{
\begin{columns}[T,onlytextwidth]
\column{0.6\textwidth}
\textcolor{blue}{Hybrid Models}
\begin{itemize}
	\item Incorporate elements of both approaches
	\item Supplement data with knowledge or priors
\end{itemize}
\column{0.4\textwidth}
\centering
\includegraphics[width=0.5\textwidth]{Figures/NS_pic.png}
\end{columns}

@@

\begin{frame}{Incorporating Knowledge of Physics into Neural Networks}
\begin{enumerate}
	\item<2-> \textbf{Symmetry Based:} incorporate symmetries and conservation laws as hard constraints into a network: E3NNs\footcite{geiger2022e3nn}, LieConv\footcite{Finzi2020}, RiCNN \footcite{chidester2018rotation}
	\item<3-> \textbf{Model Discovery Based:} use a library of terms to discover simple equations: SINDy\footcite{champion2019data}, Genetic Programming\footcite{schmidt2009distilling}
	\item<4-> \textbf{Equations Based:} incorporate first-principle models to aid training of networks: PINNs\footcite{raissi2017physics}, UDEs\footcite{rackauckas2020udes}, \textit{PINODE}
\end{enumerate}

@@

\begin{frame}{Reduced-Order Models: Data-Driven Loss}
\includegraphics[width=\textwidth]{Figures/just_rom.png}
\vspace{0.5em}

Notation:
\begin{itemize}
	\item $k$ trajectories $x_i(t_j)$, $p$ timesteps each ($i = 1, \dots, k$, $j = 1, \dots, p$)
	\item $\sigma$ -- observation noise variance
	\item $\omega_1$, $\omega_2$ -- weights (hyper-parameters) 
\end{itemize}

\begin{align}
    \LL^{data}_\theta & = \frac{1}{2\sigma^2}\sum_{i = 1}^k \left[\frac{\omega_1}{p}\sum_{j=1}^p\underbrace{\left\|\bd{x_i}(t_j) - \psi_\theta(\phi_\theta(\bd{x_i}(t_j)))\right\|^2}_{\text{reconstruction loss}}\right. + \\
     & + \left.\frac{\omega_2}{p}\sum_{j=1}^p \underbrace{\left\|\psi_\theta\left(\phi_\theta(\bd{x_i}(t_1)) + \int_{t_1}^{t_j}h(z(t))dt\right) - \bd{x_i}(t_j)\right\|^2}_{\text{prediction loss}} \right]
\end{align}

@@

\begin{frame}{Physics-Informed Loss}
%1) We introduce physics to this system by adding a term which regularizes latent gradient field. 
%2) In particular, it forces it to be equal to what a true physics should be under such projection.
%3) We can not evaluate physics everywhere but we can at particular carefully-selected points. We call these points collocation points.
%4) We feed a lot of collocation points and ask a network to do interpolation 
Using chain rule:
\only<1>{\includegraphics[width=\textwidth]{Figures/collocations_1.png}}
\only<2>{\includegraphics[width=\textwidth]{Figures/collocations_2.png}}
\only<3>{\includegraphics[width=\textwidth]{Figures/collocations_3.png}}
\only<4>{\includegraphics[width=\textwidth]{Figures/collocations_4.png}}
\only<5>{\includegraphics[width=\textwidth]{Figures/collocations_5.png}}
\only<6>{\includegraphics[width=\textwidth]{Figures/collocations_6.png}}
\only<7>{\includegraphics[width=\textwidth]{Figures/collocations_7.png}}
\end{frame}

\begin{frame}{Physics-Informed, Data-Driven, and Hybrid Models}
	Values of $\omega_1$, $\omega_2$, $\omega_3$, and $\omega_4$ control the type of the ROM:
	\begin{itemize}
		\item If $\omega_1 = \omega_2 = 0$ then $\LL_\theta^\text{data} = 0$. Thus, the model is purely \textcolor{orange}{Physics-Informed}
		\item If $\omega_3 = \omega_4 = 0$ then $\LL_\theta^\text{physics} = 0$. Thus, the model is purely \textcolor{teal}{Data-Driven}
		\item Otherwise the model is \textcolor{blue}{Hybrid}
	\end{itemize}
\end{frame}

@@

\begin{frame}{Results: Burgers' Equation}
\begin{equation}
	\begin{split}
		& u_t  + uu_x = \nu u_{xx} \\
	    & u(-\pi, t) = u(\pi, t),\quad \forall t \in [0, T], \quad \nu = 0.01
	\end{split}
\end{equation}
\uncover<2->{
\includegraphics[width=\textwidth]{Figures/burgers_examples_of_ics.pdf}
}

\only<2>{
\small
ICs and Collocations:
\begin{columns}[T,onlytextwidth]
\column{0.3\textwidth}
Harmonic:
\begin{equation*}
	\begin{split}
		& u(x) = \sum_{k=1}^{30}a_k \sin(2\pi x/k) \\ & + b_k \cos(2\pi x/k) \\
		& a_k = \alpha_ks_k \\
		& \alpha_k \sim \mathcal{U}(0, 1) \\
		& s_k \sim \mathcal{B}e(0.5)
	\end{split}
\end{equation*}

\column{0.3\textwidth}
Bell-curve:
\begin{equation*}
	\begin{split}
		& u(x) = \frac{1}{\sqrt{2\pi \sigma^2}}\exp^{\frac{-(x-x_0)^2}{2\sigma^2}} \\
		& \sigma \sim \mathcal{U}(0, 3) \\
		& x_0 \sim \mathcal{U}(-\pi, \pi) 
	\end{split}
\end{equation*}

\column{0.3\textwidth}
Bumps:
	\begin{equation*}
		\begin{split}
			& u(x) = \frac{a}{1+\exp^{-k(x-x_0)}} \\ & - \frac{a}{1 + \exp^{-k(x-x_1)}} \\
			& k \sim \mathcal{U}(5, 20) \\
			& x_0, x_1 \sim \mathcal{U}(-\pi, \pi) 
		\end{split}
	\end{equation*}
\end{columns}
}

\uncover<3->{
\includegraphics[width=\textwidth]{Figures/example_burgers.pdf}
}

@@

\begin{frame}{Single-Pixel Imaging}
	% This is how SPI setup translates into Math
	\includegraphics[width=\textwidth]{Figures/spi_math.png}
	\uncover<2->{
		\centering
		\textit{Single-Pixel Image Recovery}: find $\textbf{x}$ using $\textbf{y}$ and $\textbf{A}$.

		\vspace{1em}

		\textbf{SPF rate}, \% = Number of samples per frame / number of pixels per frame * 100
	}
\end{frame}

@@

\begin{frame}{Results: Burger's Equation}
	\uncover<1->{
	Recovery with SPF=25\%:
	\includegraphics[width=\textwidth]{Figures/cs_burgers_comparison_32.pdf}
	}
	\uncover<2->{
	Recovery with SPF=6.25\%:
	\includegraphics[width=\textwidth]{Figures/cs_burgers_comparison_8.pdf}
	}
	\uncover<3->{
	Recovery with SPF=1.5\%:
	\includegraphics[width=\textwidth]{Figures/cs_burgers_comparison_2.pdf}
	}

@@

\begin{frame}{Results: Burger's Equation}
	\includegraphics[width=\textwidth]{Figures/cs_burgers_psnr.png}
	\vspace{2em}
	Metrics:
	\begin{itemize}
		\item \textbf{PSNR}: Peak Signal-to-Noise Ratio 
		\item \textbf{RMSE}: Residual Mean Square Error
		\item \textbf{SSIM}: Structural Similarity Index Measure
	\end{itemize}
\end{frame}

\begin{frame}[label=again]{Results: Kolmogorov Flow}
	A 2D velocity field $\bd{u}(x, y, t)$:

	\begin{align}
	\label{eq:kolmogorov_flow_definition}
	& \partial_t \bd{u} + \bd{u} \cdot \nabla \bd{u} = -\nabla p + \nu\nabla^2\bd{u} + f \\
	& \nabla \cdot \bd{u} = 0
	\end{align}
	where 
	\begin{itemize}
		\item $p$ is a 2D pressure field
		\item $f = \alpha\sin(ky)x$ - driving force with amplitude $A$ and wavenumber $k$ ($k=4$)
		\item $\nu = 1/\text{Re}$ is the non-dimensional viscosity. Re=40
	\end{itemize}
	\vspace{1em}
	Reconstruction with SPF rate = $0.18$\% (8 SPI samples per a frame of $66\times 66$ pixels):  
	\animategraphics[loop,width=\textwidth]{5}{Figures/kolm_example_anim_}{0}{19}
\end{frame}

@@

\begin{frame}{Results: Gas Monitoring}
	\vspace{2em}
	Gas monitoring problem:
	\begin{itemize}
		\item 494 240$\times$320 video recordings, 10 steps each
		\item 512 samples per frame, SPF rate of 0.67\%
		\item Background noise
	\end{itemize}
	\centering
	\animategraphics[loop,width=0.6\textwidth]{5}{Figures/gas_frames_}{1}{9}
\end{frame}

\begin{frame}{Thank You!}
\includegraphics[height=35pt]{figures/sasha.png}
\includegraphics[height=35pt]{figures/jim.jpg}
\includegraphics[height=35pt]{figures/peng.jpg}
\includegraphics[height=35pt]{figures/hassan.jpg}
\includegraphics[height=35pt]{figures/saleh.jpeg}
\includegraphics[height=35pt]{figures/yuying.jpeg}
\includegraphics[height=35pt]{figures/nathan.jpg}
\includegraphics[height=35pt]{figures/steve.jpeg}
\includegraphics[height=35pt]{figures/josh.jpg}

\vspace{1em}
\textbf{Sparse Relaxed Regularized Regression for Linear Mixed-Effect Models}\\
{\small
Together with Aleksandr Aravkin, James Burke, Damian Santomauro, and Peng Zheng
\begin{itemize}
	\item ``A Relaxation Approach to Feature Selection for Linear Mixed Effects Models''\\ \textit{submitted to Journal of Computational and Graphical Statistics (JCGS)}
	\item ``Analysis of Relaxation Methods for Feature Selection in Mixed Effects Models'' \\ \textit{submitted to Journal of Computational Optimization and Applications (COAP)}
	\item ``\texttt{pysr3}: A Python Package for Spare Relaxed Regularized Regression'' \\ \textit{Journal of Open-Source Software (JOSS), 2023, ICCOPT 2022, SIAM OPT 2023}
\end{itemize}
}

\vspace{1em}
\textbf{PINODE: Physics-Informed Neural ODEs}\\
{\small
Together with Hassan Mansour, Saleh Nabi, and Yuying Liu
\begin{itemize}
	\item ``Physics-Informed Koopman Network'' \\
	\textit{SIAM ADS 2023, arXiv:2211.09419}
	\item ``Physics-Informed Neural ODE: Embedding Physics into Models using Collocation Points''\\
	\textit{Submitted to Nature Special Issue on Physics-Informed Machine Learning}
\end{itemize}
}

\vspace{1em}
\textbf{Single-Pixel Imaging with Reduced-Order Models}\\
{\small
Together with J. Nathan Kutz, Steven Brunton, Joshua Rapp, Hassan Mansour, and Saleh Nabi
\begin{itemize}
	\item ``Single pixel imaging of spatio-temporal flows using differentiable latent dynamics'' \textit{in preparation}
\end{itemize}
}
\end{frame}

@@

\appendix
\section{Appendix: $\mathcal{MSR}3$}
